---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Study Focus and Distraction Patterns
Staying focused while studying can be challenging, especially with different distractions around.
This report explores my study sessions to see how factors like phone use, study time, and types of distraction may relate to my level of focus.

```{r}
library(tidyverse)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTDpzU_Zi1tKuh8W9EZh2ylB7X5TCMLanZ8iTma6vCZG5pux4l1uZnogN2zD5dq1pZoSMe-Tg0EkTZ-/pub?gid=1107218588&single=true&output=csv")

latest_data <- logged_data %>%
  rename(
    study_time = `Q1..How.long.was.your.study.session...in.minutes.`,
    time_of_day = `Q2..What.time.of.day.did.study.session.occur.`,
    location = `Q3..Where.did.you.study.`,
    phone_use = `Q4..Did.you.use.your.phone.during.study.session.`,
    distraction = `Q5..What.was.your.main.distraction..if.any..`,
    focus = `Q6..How.would.you.rate.your.level.of.focus.`
  )

mean_time <- mean(latest_data$study_time, na.rm = TRUE)
max_time <- max(latest_data$study_time, na.rm = TRUE)
min_time <- min(latest_data$study_time, na.rm = TRUE)
total_sessions <- nrow(latest_data)

```

In total, `r total_sessions` study sessions were recorded. 
On average, each session lasted about `r round(mean_time, 1)` minutes, 
with the longest session reaching `r max_time` minutes. 
This suggests that most study sessions were of moderate length, with some longer sessions as well.

### bar chart 1
```{r}
barchart1 <- latest_data %>%
  ggplot() +
  geom_bar (aes(x = factor(focus), fill = factor(focus))) +
  labs(title = "More focus? Less focus?",
       subtitle = "Distribution of focus levels across all study sessions",
       x = "Focus Level",
       y = "Number of Study Sessions"
       )
barchart1
```

This bar chart shows how focus levels are distributed across all study sessions. 

It can be seen that certain focus levels occur more frequently than others, 
suggesting that my focus is not evenly distributed. 

In particular, focus level 4 appears the most common, indicating that I was generally able to maintain a reasonable level of concentration during most sessions.

### bar chart 2
```{r}
barchart2 <- latest_data %>%
ggplot(aes(x = phone_use, fill = factor(focus)))+
  geom_bar(position = "dodge") +
labs(title = "Does phone use relate to focus level?",
     subtitle = "Comparing phone use and focus levels across study session",
     x = "Phone Use",
     y = "Number of Study Sessions"
     )
barchart2
```

This chart compares focus levels between study sessions with and without phone use. 
Each group represents whether a phone was used, while the colors show different focus levels. 

From the chart, sessions without phone use appear to have slightly higher counts of higher focus levels, 
while sessions with phone use show more variation across lower and mid-level focus. 

This suggests that phone use may be associated with reduced concentration, although the pattern is not entirely consistent.

### bar chart 3
```{r}
barchart3 <- latest_data %>%
  ggplot(aes(x = distraction, fill = factor(focus)))+
  geom_bar(position = "dodge") +
  labs(title = "Focus Level by Type of Distraction",
       x = "Type of Distraction",
       y = "Number of Study Sessions"
  )
barchart3
```

The relationship between distraction type and focus is not very clear from this chart. 
There does not appear to be a strong or consistent pattern across different types of distraction. 

This may suggest that the impact of distraction varies depending on the situation.
